---
title: "Homework3"
author: "Chen Yi-Ju(Ernie)"
date: "2020/6/4"
output:   
  #html_document: default
  pdf_document:
    latex_engine: xelatex
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 7.1
### Describe a situation or problem from your job, everyday life, current events, etc., for which exponential smoothing would be appropriate. What data would you need? Would you expect the value of α (the first smoothing parameter) to be closer to 0 or 1, and why?

<font size="4">I would consider oil price being a good situation to use exponential smoothing. α would  be  somewhere closer to 1 than 0 because the oil price(under current situations) are known to have big fluncuations due to random events happening.<font/>

## Question 7.2
### Using the 20 years of daily high temperature data for Atlanta (July through October) from Question 6.2 (file temps.txt), build and use an exponential smoothing model to help make a judgment of whether the unofficial end of summer has gotten later over the 20 years.

### My answer is No. According to exponential smoothing, summer has not gotten latter over the 20 years.This is the proccess for proving it.<br>

Setup:
```{r ,echo = TRUE, message = FALSE, warning = FALSE}
setwd("D:/ernie/self-study/GTxMicroMasters/Introduction to Analytics Modeling/week3/homework")
library(magrittr)
library(tidyverse)
library(lubridate)
library(corrplot)
library(leaps)
```

turning data into time. series format 
```{r}
weather <- data.frame(read.table("temps.txt" , header = T))%>%
  select(.,- DAY) %>%
  unlist()%>%
  as.vector()%>%
  ts(start = 1996 , end = 2015 , frequency = 100)
```


Graphically represented: It is hard to see actual trends 
```{r}
plot(weather)
```

Putting down the HoltWinters Function
```{r}
HoltWinters(weather)
```

The main focus is here :<br>
Smoothing parameters:<br>
 alpha: 0.7015953
 beta : 0
 gamma: 0.6813504
 
 
the beta of the Holt Winters Function is 0, indicating no overall trend, which matches our intuition.


## Question 8.1
### Describe a situation or problem from your job, everyday life, current events, etc., for which a linear regression model would be appropriate. List some (up to 5) predictors that you might use.

A good opportunity would be predicting a baseball team's winning chances. It would be through parameters including: <br>
team average ERA(Earned run average)<br>
team average batting average<br>
team average slugging average<br>
and team average fielding percentage.<br>

## Question 8.2
### Using crime data , use regression (a useful R function islm or glm) to predict the observed crime rate in a cityin a city with the following data:
M = 14.0 <br>
So = 0 <br>
Ed = 10.0 <br>
Po1 = 12.0 <br>
Po2 = 15.5 <br>
LF = 0.640 <br>
M.F = 94.0 <br>
Pop = 150 <br>
NW = 1.1 <br>
U1 = 0.120 <br>
U2 = 3.6 <br>
Wealth = 3200 <br>
Ineq = 20.1 <br>
Prob = 0.04 <br>
Time = 39.0 <br>
Show your model (factors used and their coefficients), the software output, and the quality of fit. <br>

### Answer : I created a model omitting parameters that are too low in correlation with the results or are highly correlated with other parameters, making them un-independent. The model I created has an 75% R-squared value and the prediction according to the model is 1177.978. <br/>

Read Data
```{r}
crime <- read.table("uscrime.txt" , header = TRUE)%>%
  data.frame()
```

Showing the correlation between predictors
```{r}
pl1 <- corrplot(cor(crime))
```

We eliminate predictor P02 due to its  high correlation with p01<br/>

Numeric and Graphical representation of correlation with the crime variable
```{r}
cor_relation <- abs(cor(crime$Crime , crime[,1:15]))%>%
  data.frame()
cor_relation <- cor_relation%>%
  gather(predictor, correlation)
cor_relation
pl2 <- ggplot(data = cor_relation, aes( x  = predictor , y = correlation , fill = correlation )) +
  geom_col()
pl2
```

We remove NW,U1 and So due to low correlation <br/>

Constructing the model:
```{r}
model <- lm (data = crime , Crime ~ Ed + Ineq + LF + M + M.F +Po1 + Pop + Prob  + Time + Ed)
summary(model)
```

The summary results show that R- squared is at about 75% which is a good enough result. One thing to notice is however the Variables LF,M.F., Pop and Time are not statistically significant.<br>
Nevertheless, We test out the model using the given numbers:<br>
```{r}
test <- data.frame(   M = 14.0,So = 0,Ed = 10.0,Po1 = 12.0,
                      Po2 = 15.5,LF = 0.640,M.F = 94.0 ,Pop = 150,
                      NW = 1.1,U1 = 0.120,U2 = 3.6,Wealth = 3200,Ineq = 20.1,Prob = 0.04,Time = 39.0
                      )
predict(model,test)
```

Therefore my prediction is 1177.978.

